Evaluating infectious disease forecasts with allocation scoring rules

### 2023-08-29 alloscore_manuscript/allocation.tex
an attempt to remove enough content to get to something suitable for 'paper 1'

Briefly, the allocation score of a forecast is the avoidable unmet demand that results from using that forecast to set resource allocations by minimizing expected unmet need.
For example, suppose that a decision-maker is provided with forecasts of the level of need for medical resources in each of several states or hospital systems.
If there is a limited amount of the medical resource that is available to distribute, a decision-maker could choose an allocation of that resource across locations that minimizes the expected unmet need according to that forecast.
As measured by the allocation score, one forecast is better than another if it would lead decision-makers to an allocation that results in less unmet need.
%By ``unnecessary'' we mean the unmet need that could have been avoided by an oracle that knows exactly how much need will occur in each location and divides the amount $K$ so that nothing is wasted in one location while it could be put to use in another.
If the amount of resources that is available to distribute is less than the actual need, some amount of unmet demand is unavoidable.
The allocation score for a forecast does not include the unmet demand that was unavoidable given the resource constraint, and so it measures only the amount of unmet demand that could have been prevented by using a different allocation of available resources than that suggested by the forecast.
We elaborate on these ideas in Section~\ref{sec:methods}.

@@

We give a high-level review of a general procedure for developing proper scoring rules that are tailored to a specific decision-making task in section \ref{sec:methods.decisiontheory}. In section \ref{sec:methods.quantileloss} we review how quantile loss can be obtained within this framework in a setting where a decision-maker is required to determine the quantity of a good to procure while balancing the cost of purchasing an additional unit of the good with loss that may result from under-procurement. We then discuss how the continuous ranked probability score (CRPS) can be obtained as an integral of the quantile loss across values of the cost/loss ratio. These developments mirror the structure of section \ref{sec:methods.allocation}. There, we develop a novel \emph{allocation score} that is analogous to the quantile score but is suitable for evaluation of forecasts in the context of decisions about allocation of limited resources across multiple locations when the resource constraint is known. We then describe an \emph{integrated allocation score} that is analogous to the CRPS and is obtained by integrating the allocation score across values of the resource constraint.

\subsection{Overview of Allocation Scoring}

Suppose that a decision-maker is tasked with determining how much of a resource such as a medical supply should be allocated to each of $n$ locations, subject to the constraint that only $K$ units of the resource are available in total.
If the decision-maker is provided with a multivariate forecast $F$ that predicts resource demand in each location, one option is to choose the resource allocation that minimizes the expected total unmet demand according to the forecast.
We will give a more precise mathematical statement in section \ref{sec:methods.allocation}, but at a high level, the total expected unmet demand according to the forecast is
\begin{align}
\sum_{i=1}^n E_{F_i}[\text{unmet need in location $i$}],
\end{align}
where $F_i$ is the marginal forecast distribution of demand in location $i$.
This allocation problem has an intuitively appealing solution: allocate so that the probabilities of need exceeding allocation in various locations are as close to each other as possible.
This will lead to the allocations provided by $F$ being quantiles of the marginal distributions $F_i$ for some \emph{single} probability level $\tau$ that is shared in common for all locations.

After time passes and the actual level of resource need has been observed, the quality of a selected allocation can be measured by comparing the actual demand in each location to the amount of resources that were sent there. Specifically, we compute the total unmet demand that resulted from the selected allocation:
\begin{align}
    \sum_{i=1}^n \text{unmet demand in location $i$ based on the selected allocation}.
\end{align}
One allocation is better than another if it results in lower total unmet demand.

The \textbf{allocation score} of the forecast $F$ is the avoidable unmet demand that results from using the allocation that minimizes the expected unmet need according to that forecast.
By ``avoidable unmet demand'', we mean that the allocation score does not include the amount of unmet demand that was inevitable simply because the amount of available resources $K$ was less than the demand for resources.
Thus, the allocation score measures the unmet need that could have been avoided by an oracle that knows exactly how much need will occur in each location and divides the amount $K$ so that nothing is wasted in one location while it could be put to use in another. An allocation score of 0 is optimal, and indicates that no other allocation of resources could have met demand better than the allocation suggested by $F$. A larger allocation score indicates that it would have been possible to improve upon the allocation suggested by $F$.

\paragraph{Example 1} Suppose we have a forecast $F$ for demand in two locations with $F_1 = \mathrm{Exp}(1 / \sigma_1)$ and $F_2 = \mathrm{Exp}(1 / \sigma_2)$, where $\sigma_1 = 1$ and $\sigma_2 = 4$. When the marginal forecasts are exponential distributions, it can be shown that the optimal allocation divides the available resources among the locations proportionally to the scale parameters $\sigma_i$ (see section *** of the supplemental materials). If we have $K = 5$ units of our resource available, the optimal allocation according to $F$ would be 1 unit of resources in location 1 and 4 units of resources in location 2. If, on the other hand, we have $K = 10$ units available, we will allocate 2 units of resources to location 1 and 8 units to location 2. Figure~\ref{fig:exp_alloc_example} illustrates the situation.

\begin{figure}
    \includegraphics[width=\textwidth]{../figures/exponential_pred_expected_loss.pdf}
    \caption{An illustration of the resource allocation problem in Example 1. There are $n = 2$ locations, with predictive distributions $F_1 = \mathrm{Exp}(1)$ and $F_2 = \mathrm{Exp}(1/4)$. The cdfs of these distributions are illustrated in the panels at bottom and right. In the center panel, the background shading corresponds to the expected loss according to these forecasts. Diagonal black lines indicate resource constraints at $K=5$ and $K=10$ units; any point along those lines corresponds to an allocation that meets the resource constraint. For these forecasts, the optimal allocations are $(1, 4)$ for $K=5$ and $(2, 8)$ at $K=10$. These allocations are at the point on the constraint line where the expected loss is smallest, which also corresponds to the point where a level set of the expected loss surface (blue curve) is tangent to the constraint.}
    \label{fig:exp_alloc_example}
\end{figure}

Next suppose that we observe needs of 1 and 10 in locations 1 and 2, respectively.
Based on these observed needs, we can measure the quality of the allocation suggested by the forecast by calculating the amount of unmet need that resulted from that allocation over and above what was unavoidable given the resource constraint.
With $K = 5$ units of the resource, the allocation based on the forecast exactly meets the observed demand in location 1, but it leaves 6 units of need unmet in location 2.
However, working within the resource constraint, no other allocation could have done better: for example, allocating 0 units of resources to location 1 and 5 to location 2 still results in a total unmet need of 6 across both locations. Therefore, the forecast's allocation score is 0 with $K = 5$.
On the other hand, when $K = 10$, the forecast $F$'s allocation results in $10 - 8 = 2$ units of unmet need in location 2 despite leaving no need unmet in location 1.
In this case, the oracle would be able to prevent all but 1 of the total 11 units of need from going unmet, for example by allocating 1 unit of resources to location 1 and the remaining 9 units of resources to location 2.
The allocation score for the forecast when $K = 10$ would therefore be 1 (= 2 realized $-$ 1 unavoidable) in units of avoidable unmet need.

These scores illustrate a general result: allocation scores for a forecast will tend to be larger when the resource constraint is close to the observed demand, because this is when it matters most which locations are allocated more or less resources. If the resource constraint is very small, any allocation of those limited resources will result in a large amount of unmet need. If the resource constraint is very large, it becomes less important which locations receive relatively more or less resources because all locations will receive enough resources to meet their demand.

\paragraph{Example 2} Now consider a different forecast that also has exponential distributions for resource demand in each location, but that has the scale parameters $\sigma_1 = 2$ and $\sigma_2 = 8$, twice as large as the scale parameters of the forecast in Example 1. Because the optimal allocation is proportional to the scale parameters, this forecast would lead to the same optimal allocations as the forecast in Example 1, and would therefore be assigned the same allocation score.

Note the way in which these forecasts incurred a positive (i.e., non-optimal) allocation score of 1 when $K = 10$. It was not directly directly due to individual misalignments of the marginal forecasts $F_i$ with the observed needs, but rather because the allocations and observed needs were not proportional as vectors.
Restating: as far as allocation decisions are concerned, with a fixed constraint $K=10$ the fundamental problem with the forecast $F$ in Example 1 is not that it predicts a mean total resource demand of $5$ units; it is that the realized demand was 10 times as large in location 2 as in location 1, but the forecast only indicated that the resource allocation for location 2 should be 4 times the allocation for location 1.

This illustrates a fundamental property of the allocation score: at its core, it measures whether the forecast accurately captures the relative magnitudes of resource demand across different locations, which is precisely the information that is needed to allocate resources to those locations subject to a fixed resource constraint.
On the other hand, the allocation score is not directly sensitive to whether the forecasts in each location correctly capture the magnitude of resource demand in each individual location.
%For a given probability level $\tau$, if the quantiles $Q_i(\tau)$ of the marginal forecasts are proportional to the observed needs $y_i$, then the allocation score is zero for the resource constraint level $K = \sum Q_i(\tau)$.
This stands in marked contrast to other common scoring methods for multivariate forecasts that aggegate univariate scores such as CRPS or WIS for the marginal forecasts where a 
misalignment in one coordinate is penalized regardless of alignments in other coordinates. Note that we do not claim that the allocation score is generically preferable to these other scores \textemdash rather, it provides a view of forecast performance that is specifically tuned to the context of decision-making about resource allocations.

@@

\subsection{The decision-theoretic setup for forecast evaluation}
\label{sec:methods.decisiontheory}

In this section, we give an overview of the decision-theoretic setup for developing proper scoring rules that measure the value of a forecast as an input to decision making. We keep the discussion here at a somewhat informal level; we refer the reader to [some subset of Brehmer and Gneiting; Grünwald and Dawid; Dawid; Granger and Pesaran 2000; Granger and Machina 2006; Ehm et al. 2016] for more technically precise discussion.

@@

We can formalize the preceding discussion with the following three-step procedure for developing scoring rules for probabilistic forecasts:
\begin{enumerate}
\item Specify a \emph{loss function} $s(x, y)$ that measures the loss associated with taking action $x$ when outcome $y$ eventually occurs.
\item Given a probabilistic forecast $F$, determine the \emph{Bayes act} $x^F$ that minimizes the expected loss under the distribution $F$.
\item The \emph{scoring rule} for $F$ calculates the score as the loss incurred when the Bayes act was used: $S(F, y) = s(x^F, y)$.
\end{enumerate}
We use the letter $s$ for the loss function to align with the literature on evaluation of forecasts of continuous outcomes, in which context we can often identify the action $x$ with a functional (i.e., a numeric summary such as a mean or a quantile) of the forecast distribution $F$. In this context, $s$ may be used as a \emph{scoring function}. \elr{Consider moving preceding sentences to a footnote or just deleting them?}
This is a general procedure that may be applied in settings where it is possible to specify a quantitative loss function. Subject to certain technical conditions, scoring rules obtained from this procedure are proper (cite cite).

@@

\subsection{A review of quantile score, CRPS, and the weighted interval score}
\label{sec:methods.quantileloss}

We review how the quantile score arises from a particular decision-making problem in section \ref{sec:methods.quantileloss.quantile}, and how CRPS can be obtained by integrating across values of the parameters of that decision-making problem, as well as the connection to WIS, in section \ref{sec:methods.quantileloss.crps}. These results have been thoroughly discussed in the literature [cite cite cite].

\subsubsection{Decision-theoretic origins of the quantile score}
\label{sec:methods.quantileloss.quantile}

Suppose that a decision-maker is tasked with determining the quantity $x$ of a protective measure to procure; for example, $x$ might represent the number of hospital beds or amount of medicine to purchase. Additionally, suppose that each unit of this good has cost $C$ so that the total cost of procurement is $Cx$. The variable $y$ denotes the eventual realized need for this resource, e.g. the number of patients in need of a hospital bed or the amount of medication that is needed. We assume that each unit of unmet need incurs a loss denoted by $L$, so that if the selected procurement level $x$ is less than the realized need $y$, a loss of $L(x-y)$ results. At the time that a decision-maker determines the amount $x$ to procure, the demand $y$ is not yet known. We therefore define the random variable $Y$ that represents the as-yet-unknown level of demand. The forecast $F$ specifies a predictive distribution for $Y$. Here we identify $F$ with its cumulative distribution function (CDF), and $F^{-1}$ denotes the quantile function. With this formalization of the decision-making task, we can proceed to develop a proper scoring rule using the procedure outlined in section \ref{sec:methods.decisiontheory}.

\paragraph{Step 1: specify a loss function.} Combining the cost of procuring goods at level $x$ with losses due to unmet need, we arrive at the overall loss function
\begin{align}
s_Q(x,y; C, L) = Cx + L(x-y)_-.
\end{align}
Here, $(x - y)_- := \max(-(x - y),0)$ is $0$ if the amount procured, $x$, is greater than or equal to the realized demand $y$; otherwise, it is $y - x$, the amount of unmet need.

\paragraph{Step 2: Given a probabilistic forecast $F$, identify the Bayes act.} It can be shown that under the loss function $s_Q$, the Bayes act is a quantile of the forecast distribution at the probability level $\alpha = 1 - C/L$:
\begin{align}
x^F = F^{-1}(\alpha).
\end{align}
See the supplement for a verification of this result.
%In particular, faced with the classical binary decision problem of whether to recommend an additional unit of protection given a current level of protection $x$, the forecaster's optimal decision rule under $s_m$ is to recommend adding protection if $x < F^{-1}\left(1-\frac{C}{L}\right)$, that is, if
%\begin{align}
%1-F(x) = \mathbb{P}_F\{y>x\} > \frac{C}{L},
%\end{align}
%the \emph{cost-loss ratio} of the problem.

\paragraph{Step 3: Define the scoring rule.} Following the procedures outlined above, we could score the forecast distribution $F$ with the scoring rule
\begin{align*}
S_Q(F, y; C, L) &= s_Q(x^F, y; C, L) = Cx^F + L(x^F-y)_- \nonumber \\
&= C F^{-1}(\alpha) + L \left(F^{-1}(\alpha) - y\right)_- \label{eqn:S_Q_CL}
\end{align*}

We have set up the problem here in terms of the cost and loss parameters $C$ and $L$, which has the benefit of an intuitive connection to the decision-making context. However, to clarify the connection to the usual notation for the quantile loss, we can divide the loss function $s_Q$ by $L$ to obtain an expression in terms of only $\alpha$:
\begin{align*}
s_Q(x,y; \alpha) &= s_Q(x,y; C, L)/L \\
&= (C/L)x + (x-y)_- \\
&= (1 - \alpha)x + (x-y)_-.
\end{align*}
Because these loss functions are equal up to a constant of proportionality, the Bayes act is the same for both. The associated quantile scoring rule expressed in terms of $\alpha$ is
\begin{equation}
S_Q(F, y; \alpha) = (1 - \alpha)F^{-1}(\alpha) + \left(F^{-1}(\alpha) - y\right)_-. \label{eqn:S_Q_alpha}
\end{equation}
In either formulation, the key observation is that the Bayes act is the quantile of the forecast distribution $F$ at the probability level given by one minus the cost/loss ratio $C/L$.

\subsubsection{CRPS as an integrated quantile score}
\label{sec:methods.quantileloss.crps}

The scoring rule $S_Q$ of Equation \eqref{eqn:S_Q_alpha} evaluates the forecast distribution $F$ only through its $\alpha$ quantile. While this is faithful to the context of the decision-making problem, it may not be satisfying as a measure of the quality of the full forecast distribution. For this purpose, one option is to integrate the quantile scoring rule across different values of the probability level $\alpha$, weighting the probability levels according to a specified distribution $p$. This yields a weighted CRPS:
\begin{align*}
S_{CRPS}(F, y; p) &= \int S_Q(F, y; \alpha) p(\alpha) \, d\alpha.
\end{align*}
This weighted form of CRPS has appeared in the literature before, e.g. see \cite{gneiting2011weightedScoringRules}. The usual CRPS results from taking $p$ corresponding to a $\text{Uniform}(0,1)$ distribution, equally weighting all probability levels.

We emphasize that because $\alpha = 1 - C/L$, the distribution $p(\alpha)$ can be interpreted as expressing incomplete knowledge about the cost/loss ratio in the decision-making problem. The equal weighting used by the ordinary CRPS may be appropriate in the absence of any knowledge about the context in which forecasts will be used to support decision-making, but may be inappropriate if more information is known about the cost/loss ratio for a specific decision-making task.

The weighted interval score (WIS) is often used when the full forecast distribution $F$ is not available, as in the U.S. COVID-19 Forecast Hub and similar efforts where forecasts are represented by a collection of prediction intervals. WIS is a discrete approximation to CRPS, and can be obtained by using a distribution $p$ that has point masses at the probability levels corresponding to the endpoints of a finite set of prediction intervals.

@@

\subsection{The allocation score}
\label{sec:methods.allocation}

\elr{If we like the organization of the previous subsection into two subsubsections about the quantile score and the CRPS, we should replicate that here.}

We now develop a scoring rule for probabilistic forecasts that measures the value of a forecast as an input to decision making about how to allocate limited resources to meet demand across multiple locations. As a concrete example, we take the resource to be a good such as ventilators or oxygen supply. An administrator is tasked with determining where to send these resources so as to meet demand among hospital patients in different facilities or states. In contrast to the decision-making problem in the previous section, the administrator is not able to control the total amount of supply; rather, their task is to determine how to allocate the fixed supply to different locations. Following the structure of the discussion for the quantile score and CRPS, we first discuss the set up for a single value of the resource constraint $K$, which plays a role that is analogous to the cost/loss ratio for the quantile score, and then we discuss the possibility of integrating (or averaging) across values of $K$.

\subsubsection{The allocation score for a fixed resource constraint}

>>>>

Briefly, the allocation score of a forecast is the avoidable unmet need that results from using that forecast to set resource allocations by minimizing expected unmet need.
For example, suppose that a decision-maker is provided with forecasts of the level of need for medical resources in each of several states or hospital systems.
If there is a limited amount of the medical resource that is available to distribute, a decision-maker could choose an allocation of that resource across locations that minimizes the expected unmet need according to that forecast.
As measured by the allocation score, one forecast is better than another if it would lead decision-makers to an allocation that results in less unmet need.
%By ``unnecessary'' we mean the unmet need that could have been avoided by an oracle that knows exactly how much need will occur in each location and divides the amount $K$ so that nothing is wasted in one location while it could be put to use in another.
If the amount of resources that is available to distribute is less than the actual need, some amount of unmet need is unavoidable.
The allocation score for a forecast does not include the unmet need that was unavoidable given the resource constraint, and so it measures only the amount of unmet need that could have been prevented by using a different allocation of available resources than that suggested by the forecast.
We elaborate on these ideas in Section~\ref{sec:methods}.

@@

We begin with an informal description of the allocation score and some examples illustrating its key characteristics in section \ref{sec:methods.overview}. In section \ref{sec:methods.detailed} we develop the allocation score more carefully, building on decision-theoretic procedures for deriving proper scoring rules. We then comment on some connections between the allocation score that we propose and other common scores that can be derived from decision-theoretic foundations, such as the quantile score, WIS, and CRPS, in section \ref{sec:methods.related}.

\subsection{Overview of Allocation Scoring}
\label{sec:methods.overview}

Suppose that a decision-maker is tasked with determining how much of a resource such as a medical supply should be allocated to each of $N$ locations, subject to the constraint that only $K$ units of the resource are available.
If the decision-maker is provided with a multivariate forecast $F$ that predicts resource need in each location, one option is to choose the resource allocation that minimizes the expected total unmet need according to the forecast.
We will give a more precise mathematical statement in section \ref{sec:methods.allocation}, but informally, the total expected unmet need according to the forecast is
\begin{align}
\sum_{i=1}^N E_{F_i}[\text{unmet need in location $i$}], \label{eqn:informal_objective}
\end{align}
where $F_i$ is the marginal forecast distribution of need in location $i$ and the unmet need in a particular location is the difference between resource need in that location and the number of resources that were allocated there.
This allocation problem has an intuitively appealing solution: allocate so that the probabilities of need exceeding allocation in various locations are as close to each other as possible.
This will lead to the allocations provided by $F$ being quantiles of the marginal distributions $F_i$ for some \emph{single} probability level $\tau$ that is shared in common for all locations.

After time passes and the actual level of resource need has been observed, the quality of a selected allocation can be measured by comparing the actual need in each location to the amount of resources that were sent there. Specifically, we compute the total unmet need that resulted from the selected allocation:
\begin{align}
    \sum_{i=1}^N \text{unmet need in location $i$}. \label{eqn:informal_loss}
\end{align}
We emphasize that in Equation \eqref{eqn:informal_loss} the calculation of unmet need is based on the actual resource need that was realized in each location, while in Equation \eqref{eqn:informal_objective} the calculation of unmet need was based on a hypothetical potential future level of resource need.
Once the actual levels of resource need have been observed, we can obtain a quantitative measure of the quality of alternative allocation decisions: one allocation is better than another if it results in lower total unmet need.

The \textbf{allocation score} of the forecast $F$ is the avoidable unmet need that results from using the allocation that minimizes the expected unmet need according to that forecast.
By ``avoidable unmet need'', we mean that the allocation score does not include the amount of unmet need that was inevitable simply because the amount of available resources $K$ was less than the need for resources.
Rather, the allocation score measures the unmet need that could have been avoided by an oracle that knows exactly how much need will occur in each location and divides the amount $K$ so that nothing is wasted in one location while it could be put to use in another. An allocation score of 0 is optimal, and indicates that no other allocation of resources could have met need better than the allocation suggested by $F$. A larger allocation score indicates that it would have been possible to improve upon the allocation suggested by $F$.

\paragraph{Example 1} Suppose we have a forecast $F$ for need in two locations with $F_1 = \mathrm{Exp}(1 / \sigma_1)$ and $F_2 = \mathrm{Exp}(1 / \sigma_2)$, where $\sigma_1 = 1$ and $\sigma_2 = 4$. When the marginal forecasts are exponential distributions, it can be shown that the optimal allocation divides the available resources among the locations proportionally to the scale parameters $\sigma_i$ (see section *** of the supplemental materials). If we have $K = 5$ units of our resource available, the optimal allocation according to $F$ would be 1 unit of resources in location 1 and 4 units of resources in location 2. If, on the other hand, we have $K = 10$ units available, we will allocate 2 units of resources to location 1 and 8 units to location 2. Figure~\ref{fig:exp_alloc_example} illustrates the situation.

\begin{figure}
    \includegraphics[width=\textwidth]{../figures/exponential_pred_expected_loss.pdf}
    \caption{An illustration of the resource allocation problem in Example 1. There are $N = 2$ locations, with predictive distributions $F_1 = \mathrm{Exp}(1)$ and $F_2 = \mathrm{Exp}(1/4)$. The cdfs of these distributions are illustrated in the panels at bottom and right. In the center panel, the background shading corresponds to the expected loss according to these forecasts. Diagonal black lines indicate resource constraints at $K=5$ and $K=10$ units; any point along those lines corresponds to an allocation that meets the resource constraint. For these forecasts, the optimal allocations are $(1, 4)$ for $K=5$ and $(2, 8)$ at $K=10$. These allocations are at the point on the constraint line where the expected loss is smallest, which also corresponds to the point where a level set of the expected loss surface (blue curve) is tangent to the constraint.}
    \label{fig:exp_alloc_example}
\end{figure}

Next suppose that we observe needs of 1 and 10 in locations 1 and 2, respectively.
Based on these observed needs, we can measure the quality of the allocation suggested by the forecast by calculating the amount of unmet need that resulted from that allocation over and above what was unavoidable given the resource constraint.
With $K = 5$ units of the resource, the allocation based on the forecast exactly meets the observed need in location 1, but it leaves 6 units of need unmet in location 2.
However, working within the resource constraint, no other allocation could have done better: for example, allocating 0 units of resources to location 1 and 5 to location 2 still results in a total unmet need of 6 across both locations. Therefore, the forecast's allocation score is 0 with $K = 5$.
On the other hand, when $K = 10$, the forecast $F$'s allocation results in $10 - 8 = 2$ units of unmet need in location 2 despite leaving no need unmet in location 1.
In this case, the oracle would be able to prevent all but 1 of the total 11 units of need from going unmet, for example by allocating 1 unit of resources to location 1 and the remaining 9 units of resources to location 2.
The allocation score for the forecast when $K = 10$ would therefore be 1 (= 2 realized $-$ 1 unavoidable) in units of avoidable unmet need.

These scores illustrate a general result: allocation scores for a forecast will tend to be larger when the resource constraint is close to the observed need, because this is when it matters most which locations are allocated more or less resources. If the resource constraint is very small, any allocation of those limited resources will result in a large amount of unmet need. If the resource constraint is very large, it becomes less important which locations receive relatively more or less resources because all locations will receive enough resources to meet their need.

\paragraph{Example 2} Now consider a different forecast that also has exponential distributions for resource need in each location, but that has the scale parameters $\sigma_1 = 2$ and $\sigma_2 = 8$, twice as large as the scale parameters of the forecast in Example 1. Because the optimal allocation is proportional to the scale parameters, this forecast would lead to the same optimal allocations as the forecast in Example 1, and would therefore be assigned the same allocation score.

Note the way in which these forecasts incurred a positive (i.e., non-optimal) allocation score of 1 when $K = 10$. It was not directly directly due to individual misalignments of the marginal forecasts $F_i$ with the observed needs, but rather because the allocations and observed needs were not proportional as vectors.
Restating: as far as allocation decisions are concerned, with a fixed constraint $K=10$ the fundamental problem with the forecast $F$ in Example 1 is not that it predicts a mean total resource need of $5$ units; it is that the realized need was 10 times as large in location 2 as in location 1, but the forecast only indicated that the resource allocation for location 2 should be 4 times the allocation for location 1.

This illustrates a fundamental property of the allocation score: at its core, it measures whether the forecast accurately captures the relative magnitudes of resource need across different locations, which is precisely the information that is needed to allocate resources to those locations subject to a fixed resource constraint.
On the other hand, the allocation score is not directly sensitive to whether the forecasts in each location correctly capture the magnitude of resource need in each individual location.
%For a given probability level $\tau$, if the quantiles $Q_i(\tau)$ of the marginal forecasts are proportional to the observed needs $y_i$, then the allocation score is zero for the resource constraint level $K = \sum Q_i(\tau)$.
This stands in marked contrast to other common scoring methods for multivariate forecasts that aggregate univariate scores such as CRPS or WIS for the marginal forecasts where a 
misalignment in one coordinate is penalized regardless of alignments in other coordinates. Note that we do not claim that the allocation score is generically preferable to these other scores \textemdash rather, it provides a view of forecast performance that is specifically tuned to the context of decision-making about resource allocations.

@@

\subsection{A decision-theoretic development of the allocation score}
\label{sec:methods.detailed}

We give a high-level review of a general procedure for developing proper scoring rules that are tailored to specific decision-making tasks in section \ref{sec:methods.detailed.decisiontheory}, and then in section \ref{sec:methods.detailed.allocation} we apply that procedure to develop the allocation score based on the task of deciding on how to allocate a fixed supply of resources across multiple locations.

\subsubsection{The decision-theoretic setup for forecast evaluation}
\label{sec:methods.detailed.decisiontheory}

%In this section, we give an overview of the decision-theoretic setup for developing proper scoring rules that measure the value of a forecast as an input to decision making. We keep the discussion here at a somewhat informal level; we refer the reader to [some subset of Brehmer and Gneiting; Grünwald and Dawid; Dawid; Granger and Pesaran 2000; Granger and Machina 2006; Ehm et al. 2016] for more technically precise discussion.

@@

We can formalize the preceding discussion with the following three-step procedure for developing scoring rules for probabilistic forecasts:
\begin{enumerate}
\item Specify a \emph{loss function} $s(x, y)$ that measures the loss associated with taking action $x$ when outcome $y$ eventually occurs.
\item Given a probabilistic forecast $F$, determine the \emph{Bayes act} $x^F$ that minimizes the expected loss under the distribution $F$.
\item The \emph{scoring rule} for $F$ calculates the score as the loss incurred when the Bayes act was used: $S(F, y) = s(x^F, y)$.
\end{enumerate}
%We use the letter $s$ for the loss function to align with the literature on evaluation of forecasts of continuous outcomes, in which context we can often identify the action $x$ with a functional (i.e., a numeric summary such as a mean or a quantile) of the forecast distribution $F$. In this context, $s$ may be used as a \emph{scoring function}. \elr{Consider moving preceding sentences to a footnote or just deleting them?}
This is a general procedure that may be applied in settings where it is possible to specify a quantitative loss function. Subject to certain technical conditions, scoring rules obtained from this procedure are proper. We refer the reader to [some subset of Brehmer and Gneiting; Grünwald and Dawid; Dawid; Granger and Pesaran 2000; Granger and Machina 2006; Ehm et al. 2016] for more technically precise discussion.

@@

% \subsection{A review of quantile score, CRPS, and the weighted interval score}
% \label{sec:methods.quantileloss}

% We review how the quantile score arises from a particular decision-making problem in section \ref{sec:methods.quantileloss.quantile}, and how CRPS can be obtained by integrating across values of the parameters of that decision-making problem, as well as the connection to WIS, in section \ref{sec:methods.quantileloss.crps}. These results have been thoroughly discussed in the literature [cite cite cite].

% \subsubsection{Decision-theoretic origins of the quantile score}
% \label{sec:methods.quantileloss.quantile}

% Suppose that a decision-maker is tasked with determining the quantity $x$ of a protective measure to procure; for example, $x$ might represent the number of hospital beds or amount of medicine to purchase. Additionally, suppose that each unit of this good has cost $C$ so that the total cost of procurement is $Cx$. The variable $y$ denotes the eventual realized need for this resource, e.g. the number of patients in need of a hospital bed or the amount of medication that is needed. We assume that each unit of unmet need incurs a loss denoted by $L$, so that if the selected procurement level $x$ is less than the realized need $y$, a loss of $L(x-y)$ results. At the time that a decision-maker determines the amount $x$ to procure, the demand $y$ is not yet known. We therefore define the random variable $Y$ that represents the as-yet-unknown level of demand. The forecast $F$ specifies a predictive distribution for $Y$. Here we identify $F$ with its cumulative distribution function (CDF), and $F^{-1}$ denotes the quantile function. With this formalization of the decision-making task, we can proceed to develop a proper scoring rule using the procedure outlined in section \ref{sec:methods.decisiontheory}.

% \paragraph{Step 1: specify a loss function.} Combining the cost of procuring goods at level $x$ with losses due to unmet need, we arrive at the overall loss function
% \begin{align}
% s_Q(x,y; C, L) = Cx + L(x-y)_-.
% \end{align}
% Here, $(x - y)_- := \max(-(x - y),0)$ is $0$ if the amount procured, $x$, is greater than or equal to the realized demand $y$; otherwise, it is $y - x$, the amount of unmet need.

% \paragraph{Step 2: Given a probabilistic forecast $F$, identify the Bayes act.} It can be shown that under the loss function $s_Q$, the Bayes act is a quantile of the forecast distribution at the probability level $\alpha = 1 - C/L$:
% \begin{align}
% x^F = F^{-1}(\alpha).
% \end{align}
% See the supplement for a verification of this result.
% %In particular, faced with the classical binary decision problem of whether to recommend an additional unit of protection given a current level of protection $x$, the forecaster's optimal decision rule under $s_m$ is to recommend adding protection if $x < F^{-1}\left(1-\frac{C}{L}\right)$, that is, if
% %\begin{align}
% %1-F(x) = \mathbb{P}_F\{y>x\} > \frac{C}{L},
% %\end{align}
% %the \emph{cost-loss ratio} of the problem.

% \paragraph{Step 3: Define the scoring rule.} Following the procedures outlined above, we could score the forecast distribution $F$ with the scoring rule
% \begin{align*}
% S_Q(F, y; C, L) &= s_Q(x^F, y; C, L) = Cx^F + L(x^F-y)_- \nonumber \\
% &= C F^{-1}(\alpha) + L \left(F^{-1}(\alpha) - y\right)_- \label{eqn:S_Q_CL}
% \end{align*}

% We have set up the problem here in terms of the cost and loss parameters $C$ and $L$, which has the benefit of an intuitive connection to the decision-making context. However, to clarify the connection to the usual notation for the quantile loss, we can divide the loss function $s_Q$ by $L$ to obtain an expression in terms of only $\alpha$:
% \begin{align*}
% s_Q(x,y; \alpha) &= s_Q(x,y; C, L)/L \\
% &= (C/L)x + (x-y)_- \\
% &= (1 - \alpha)x + (x-y)_-.
% \end{align*}
% Because these loss functions are equal up to a constant of proportionality, the Bayes act is the same for both. The associated quantile scoring rule expressed in terms of $\alpha$ is
% \begin{equation}
% S_Q(F, y; \alpha) = (1 - \alpha)F^{-1}(\alpha) + \left(F^{-1}(\alpha) - y\right)_-. \label{eqn:S_Q_alpha}
% \end{equation}
% In either formulation, the key observation is that the Bayes act is the quantile of the forecast distribution $F$ at the probability level given by one minus the cost/loss ratio $C/L$.

% \subsubsection{CRPS as an integrated quantile score}
% \label{sec:methods.quantileloss.crps}

% The scoring rule $S_Q$ of Equation \eqref{eqn:S_Q_alpha} evaluates the forecast distribution $F$ only through its $\alpha$ quantile. While this is faithful to the context of the decision-making problem, it may not be satisfying as a measure of the quality of the full forecast distribution. For this purpose, one option is to integrate the quantile scoring rule across different values of the probability level $\alpha$, weighting the probability levels according to a specified distribution $p$. This yields a weighted CRPS:
% \begin{align*}
% S_{CRPS}(F, y; p) &= \int S_Q(F, y; \alpha) p(\alpha) \, d\alpha.
% \end{align*}
% This weighted form of CRPS has appeared in the literature before, e.g. see \cite{gneiting2011weightedScoringRules}. The usual CRPS results from taking $p$ corresponding to a $\text{Uniform}(0,1)$ distribution, equally weighting all probability levels.

% We emphasize that because $\alpha = 1 - C/L$, the distribution $p(\alpha)$ can be interpreted as expressing incomplete knowledge about the cost/loss ratio in the decision-making problem. The equal weighting used by the ordinary CRPS may be appropriate in the absence of any knowledge about the context in which forecasts will be used to support decision-making, but may be inappropriate if more information is known about the cost/loss ratio for a specific decision-making task.

% The weighted interval score (WIS) is often used when the full forecast distribution $F$ is not available, as in the U.S. COVID-19 Forecast Hub and similar efforts where forecasts are represented by a collection of prediction intervals. WIS is a discrete approximation to CRPS, and can be obtained by using a distribution $p$ that has point masses at the probability levels corresponding to the endpoints of a finite set of prediction intervals.

@@

% \subsection{The allocation score}
% \label{sec:methods.allocation}

%\elr{If we like the organization of the previous subsection into two subsubsections about the quantile score and the CRPS, we should replicate that here.}

% We now give a more formal derivation of the allocation score starting from the set up of a decision making problem about how to allocate limited resources to meet demand across multiple locations. In section \ref{sec:methods.allocation.special}, we consider a setting where the resource constraint is known, which will result in a score that is specialized to a particular quantile of the forecasts. Then in sction \ref{sec.methods.allocation.integrated}, we allow for the possibility of decision making under uncertainty about the precise value of the resource constraint, which will lead to averaging the specialized allocation score across multiple quantile levels.

%As a concrete example, we take the resource to be a good such as ventilators or oxygen supply. An administrator is tasked with determining where to send these resources so as to meet demand among hospital patients in different facilities or states. In contrast to the decision-making problem in the previous section, the administrator is not able to control the total amount of supply; rather, their task is to determine how to allocate the fixed supply to different locations. Following the structure of the discussion for the quantile score and CRPS, we first discuss the set up for a single value of the resource constraint $K$, which plays a role that is analogous to the cost/loss ratio for the quantile score, and then we discuss the possibility of integrating (or averaging) across values of $K$.

\subsubsection{The allocation score for a fixed resource constraint}
\label{sec:methods.detailed.specific_allocation}
